\documentclass[12pt]{spieman}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}


% ---------------------------------------------------------------------------------------
% BEGIN TITLE AND AUTHORS
% ---------------------------------------------------------------------------------------

\title{SPIE journal papers: sample manuscript showing style and formatting specifications}

\author[a]{Colin T. Sullender}
\author[a]{Adam Santorelli}
\author[a]{Christopher Smith}
\author[a]{Lisa M. Richards}
\author[a,*]{Andrew K. Dunn}
\affil[a]{The University of Texas at Austin, Department of Biomedical Engineering, 107 W. Dean Keeton St. Stop C0800, Austin, TX, 78712, USA}


% ----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
% ----------------------------------------------------------------------------------------
\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table}
\begin{document}
\maketitle


% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}

\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Andrew K. Dunn \linkable{adunn@utexas.edu}}

\begin{spacing}{2}


% ----------------------------------------------------------------------------------------
% BEGIN INTRODUCTION SECTION
% ----------------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}


% ----------------------------------------------------------------------------------------
% BEGIN METHODS SECTION
% ----------------------------------------------------------------------------------------
\section{Methods}
\label{sect:methods}


% ----------------------------------------------------------------------------------------
% BEGIN RESULTS SECTION
% ----------------------------------------------------------------------------------------
\section{Results}
\label{sect:results}


% ----------------------------------------------------------------------------------------
% BEGIN DISCUSSION SECTION
% ----------------------------------------------------------------------------------------
\section{Discussion}
\label{sect:discussion}


% ----------------------------------------------------------------------------------------
% BEGIN CONCLUSION SECTION
% ----------------------------------------------------------------------------------------
\section{Conclusion}
\label{sect:conclusion}


% ----------------------------------------------------------------------------------------
% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------------------
\subsection*{Disclosures}
Conflicts of interest should be declared under a separate header. If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.

\subsection* {Acknowledgments}
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding. 

\subsection* {Data, Materials, and Code Availability} 
As relevant, the availability of data, materials, and/or software code used in the research results reported in the manuscript may be declared in this section. (Note: this section is required for the \textit{Journal of Biomedical Optics} and \textit{Neurophotonics}.) Provide specific access information or restrictions for data, materials, and computer code (i.e., links to repository access addresses with guidance on commercial or public access).


% ----------------------------------------------------------------------------------------
% BEGIN BIBLIOGRAPHY
% ----------------------------------------------------------------------------------------
\bibliography{bibliography}
\bibliographystyle{spiejour}


% ----------------------------------------------------------------------------------------
% AUTHOR BIOGRAPHIES
% ----------------------------------------------------------------------------------------
\vspace{1ex}
\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.


% ----------------------------------------------------------------------------------------
% FIGURE AND TABLE LISTS
% ----------------------------------------------------------------------------------------
\listoffigures
\listoftables


% ----------------------------------------------------------------------------------------
% END
% ----------------------------------------------------------------------------------------
\end{spacing}
\end{document}
